\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-12-17 public/paper/pyg4ometry.tex
another worindg

\subsection{Tessellation of solids (meshing)}
Creating a uniform 3D mesh description of all solids (including Booleans) is exceptionally useful for visualisation and other algorithms, such as overlap
detection. For each Geant4 solid instance a triangular tessellated vertex-face mesh is generated and cached. This mesh is then used to determine the extent
of placed instances of geometry (physical volumes) and meshes for CSG-derived solids. CSG mesh calculations are performed using a Binary Space Partitioning
(BSP) tree technique in pure Python~\cite{pycsg} or via the Computational
Geometry Algorithms Library (CGAL) surface meshes~\cite{cgal:bsmf-sm-20b}
in C++. The pure Python CSG backend is further accelerated by compiling it
to C using Cython\cite{cython}.
For maximum flexibility either backend can be used, but in general, the CGAL implementation is one to two orders of magnitude faster than the Cythonized CSG implementation and must be used for large geometries.
Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to file
various polygon mesh algorithms  from CGAL~\cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.

>>>>

\subsection{Tessellation of solids (meshing)}
Creating a uniform 3D mesh description of all solids (including Booleans) is exceptionally useful for visualisation and other algorithms, such as overlap
detection. For each Geant4 solid instance a triangular tessellated vertex-face mesh is generated and cached. This mesh is then used to determine the extent
of placed instances of geometry (physical volumes) and meshes for CSG-derived solids. CSG mesh calculations are performed using a Binary Space Partitioning
(BSP) tree technique in pure Python~\cite{pycsg} or via the Computational
Geometry Algorithms Library (CGAL) surface meshes~\cite{cgal:bsmf-sm-20b}
in C++. The pure Python CSG backend is further accelerated by compiling it
to C using Cython\cite{cython}.
For maximum flexibility either backend can be used, but in general, the
CGAL implementation is one to two orders of magnitude faster than the
Cythonized CSG implementation and should be used for large geometries.
Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to file
various polygon mesh algorithms  from CGAL~\cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.
